---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.retina = TRUE,
  dpi = 300,
  out.width = "100%"
)
```

# Reproduction of NREL's ReEDS-2.0 in energyRt

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of ReEDS is to recreate the National Renewable Energy Laboratory's [Regional Energy Deployment System (ReEDS)](https://github.com/NREL/ReEDS-2.0) model in [energyRt](https://energyrt.org/), a model generator and make it available for R, energyRt, and USENSYS users as an option to apply ReEDS data or the reproduced model itself to their projects.\
The repository is organized as an R-package and will contain the following components:\
1. Data: ReEDS data and data processing functions.\
2. Model: reproduced in `energyRt` model objects using the ReEDS data.\
3. Maps: spatial data for the ReEDS model.\
4. Reporting functions, methods, and examples.\

The package will not be published on CRAN due to the data size limits.\


## Installation

The package is under development and not yet ready for use.
You can install the development version of ReEDS from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("usensys/ReEDS")
```

## Example

Currenlty, the package contains the ReEDS-2.0 regions and transmission maps.\

```{r example, fig.height=5, fig.cap="ReEDS-2.0 regions."}
# library(usensys)
library(ReEDS)
library(sf)
library(ggplot2)

# maps from ReEDS-2.0 repository, stored in `reed_maps` list-object
#see `?reeds_maps` for details
reeds_maps$US_CAN_MEX_PCA_sf |> st_drop_geometry() |> head()

plot(reeds_maps$US_CAN_MEX_PCA_sf["rb"])
```

```{r, fig.height=5, fig.cap="ReEDS-2.0 existing transmission routes and endpoints."}
ggplot() +
  geom_sf(data = reeds_maps$US_CAN_MEX_PCA_sf, color = "grey", fill = "wheat") +
  geom_sf(data = reeds_maps$transmission_routes_sf, color = "dodgerblue") +
  geom_sf(data = reeds_maps$transmission_endpoints_sf, color = "red", size = .5) +
  theme_void()

```

```{r, fig.height=5, fig.cap="ReEDS-2.0 new transmission routes"}
ggplot() +
  geom_sf(data = reeds_maps$US_CAN_MEX_PCA_sf, 
          color = "grey", fill = "wheat") +
  geom_sf(data = reeds_maps$transmission_routes_500kV, 
          aes(color = voltage, linewidth = voltage),
          alpha = .75) +
  scale_color_manual(
    values = c("500kV AC" = "dodgerblue", "500kV DC" = "red"), 
    name = "") +
  scale_linewidth_manual(
    values = c("500kV AC" = 2, "500kV DC" = .5), 
    name = "") +
  geom_sf(data = reeds_maps$transmission_endpoints_sf, 
          color = "gold", size = .5) +
  theme_void()
```

## References
ReEDS-2.0 repository: [NREL/ReEDS-2.0](https://github.com/NREL/ReEDS-2.0)\
USENSYS docs and repository: [usensys](https://www.usensys.org/)\
energyRt docs and repository: [energyRt](https://energyrt.org/)\
